\makefrontsidebar
%-------------------------------------------------------------------------------
%                   TABLE ENTRIES RIGHT COLUMN FIRST PAGE
%-------------------------------------------------------------------------------
\cvsection{Education}
\begin{cvtable}[1.5]
	\cvitem{2017 -- now*}{Master's degree}{
	    \href{https://telecos.upc.edu/en/school}{Universitat Politècnica de Catalunya - ETSETB}}{
	    \href{https://telecos.upc.edu/en/study-programs/masters/masters-degree-in-electronic-engineering-mee}{Electronic Engineering}\newline \footnotesize *Only the Master Thesis remaining.}
	\cvitem{2013 -- 2017}{Bachelor's degree}{
	    \href{https://www.uab.cat/web/universitat-autonoma-de-barcelona-1345467954774.html}{Universitat Autònoma de Barcelona}}{
	    \href{https://www.uab.cat/web/estudiar/ehea-degrees/general-information-1216708259085.html?param1=1263367118156}{Nanoscience and Nanotechnology}}
	\cvitem{}{Final Project:}{
	    \href{http://www.imb-cnm.csic.es/index.php/en/}{Institut de Microelectrònica de Barcelona - CNM}}{
    	Improvements on a portable spectrophotometer for the detection of groundwater pollution.}
	\cvitem{1998 -- 2013}{Kindergarten to High school}{
	    \href{https://santnicolau.com/}{Escola Sant Nicolau}}{
	    Specializing in technology on the later years.}
\end{cvtable}


\cvsection{Work Experience}
\cvsubsection{Employee}
\begin{cvtable}[1.5]
	\cvitem{2017 -- now}{Logistics \& Commercial Agent}{
	    \href{https://santnicolau.com/}{Fundació Sant Nicolau}}{
		Wide range of responsibilities related to a sport club's activities. From managing the sponsorship deals, to logistics of sports events; as well as week to week scheduling of matches and other tasks.}
	\cvitem{2016 -- now}{Official Statistician}{
	    \href{http://www.acb.com/}{ACB} \& \href{https://www.euroleague.net/}{Euroleague}}{
		Recording of the official statistics in \href{http://www.acb.com/}{\textit{ACB}} and \href{https://www.euroleague.net/}{\textit{Euroleague}} matches. Critical data entry in high tension environments such as the stadiums of \href{https://www.fcbarcelona.com/en/}{\textit{F.C. Barcelona}} and \href{https://www.penya.com/ca/}{\textit{C. Joventut de Badalona}}.}
	\cvitem{2016 -- 2017}{Intern}{
	    \href{http://www.imb-cnm.csic.es/index.php/en/}{Institut de Microelectrònica de Barcelona - CNM}}{
	    \href{http://www.imb-cnm.csic.es/index.php/en/research/research-groups/integrated-circuits-and-systems}{\textit{Integrated Circuits and Systems}} research group. The research developed during this period is included in the Bachelor's degree Final Project.}
	\cvitem{2010 -- now}{Basketball Coach}{
	    \href{http://www.cesantnicolau.com/cesn/}{C.E. Sant Nicolau} \& \href{https://ceglobalbasket.blog/}{C.E. Global Basket} \& \href{https://esportadaptat.org/}{FCEDF}}{
		Coaching both basketball and wheelchair-basketball players from 7 to 40 years old in different stages of their development. Participation in international tournaments with the \textit{Catalan National Team} as assistant coach as well as head coach of the \textit{Under-22 National Team}.}
\end{cvtable}
\cvsubsection{Volunteer}
\begin{cvtable}[1.5]
	\cvitem{2017 -- now}{Logistics \& Media Agent}{
	    \href{https://www.basquetsantjulia.org/?lang=en}{A.B. Sant Julià de Vilatorta}}{
		Helping in the organization of the main basketball tournament in Spain with logistics and media coverage as well as numerous other tasks. Bringing top \href{https://www.ncaa.com/sports/basketball-men/d1}{\textit{NCAA}}'s and \href{http://www.acb.com/}{\textit{ACB}}'s teams as well as hundreds of local teams to the tournament.}
\end{cvtable}


\cvsection{Awards}
\begin{cvtable}[1]
	\cvitem{\hfill2007}{\href{http://www.estalmat.org/}{ESTALMAT Catalunya}}{
	    \href{https://scm.iec.cat/}{Societat Catalana de Matemàtiques} \& \href{https://feemcat.org/}{FEEMCAT}}{
	    Selected for the 5\textsuperscript{th} edition of the \href{http://www.cangur.org/estalmat/indexcat.php}{\textit{ESTALMAT Catalunya}} project (\href{http://www.estalmat.org/}{\textit{Stimulus of Mathematical Talent}}) as one of the youngest members of the promotion.}
\end{cvtable}

\cvsection{Certifications}
\begin{cvtable}[1]
	\cvitem{\hfill2014}{
	    \href{https://www.coe.int/en/web/common-european-framework-reference-languages}{\flag{GB} B2 English Certificate}}{
	\href{https://www.uab.cat/web/uab-languages-1345709197130.html}{Universitat Autònoma de Barcelona}}{}
	\cvitem{\hfill2014}{\bodyicon{\faCar} B-Class Driving License}{\href{http://www.dgt.es/es/}{Dirección General de Tráfico}}{}
	\cvitem{\hfill2011}{\cvtexicon{basketball}0-Level Coaching License}{\href{https://www.basquetcatala.cat/}{Federació Catalana de Basquetbol}}{}
\end{cvtable}

\cvsection{Interests}
\begin{cvtable}[1.5]
    \cvitem{\hfill\bodyicon{\faCode}}{Coding}{}{
        Carles enjoys coding and has created numerous small programs to ease his work-flow during his free time.}
    \cvitem{\hfill\bodyicon{\faBook}}{Reading}{}{
        Fantasy books and historical fiction are the two main genres that managed to obtain a permanent spot on Carles's reading queue.}
    \cvitem{\hfill\bodyicon{\faFilm}}{Cinema}{}{
        When Carles needs to clear his mind, a good film is always by his side.}
\end{cvtable}
